\documentclass{muratcan_cv}

\setname{Michael}{Metternich}
\setaddress{Amsterdam/Netherlands}
\setmobile{+31 617128681}
\setmail{michael.j.metternich@gmail.com}
\setposition{Work Student} %ignored for now
\setlinkedinaccount{https://www.linkedin.com/in/mjmetter} %you can play with color of the template (red is also nice..)
\setgithubaccount{https://github.com/mjmetter} %you can play with color of the template (red is also nice..)
\setthemecolor{blue} %you can play with color of the template (red is also nice..)

\begin{document}
%Set variables
%You can add sections, texts, explanations just by copying the style below. Replace the dummy texts "\lipsum[1][x-x]\par" with actual texts.
%Create header
\headerview
\vspace{1ex}
%Sections
%
% Summary
\addblocktext{Summary}{%
Dad, developer, manager. Love making great software, but absolutely hate it when processes are considered more important than the people making it.
}
%
% Experience
\section{Experience}
    %
    \datedexperience{Bloomreach}{April 2019-present} 
    \explanation{Director of Engineering} 
    \explanationdetail{\coloredbullet\ %
     Platform-level development, operations and L2 + L3 support for \href{https://documentation.bloomreach.com/discovery/docs/documentation-overview}{Bloomreach Discovery} and \href{https://documentation.bloomreach.com/content/docs/documentation-overview}{Content}
     }    %
    \explanationdetail{\coloredbullet\ %
     Reduced hosting cost from \$ 1.5M to less than \$1M per month.
     }    %
    \explanationdetail{\coloredbullet\ %
     Pushed for and rebuilt entire Infrastructure for leading Product.
     }    %
    \explanationdetail{\coloredbullet\ %
     Leading, mentoring, and hiring high-performing leaders and staff architects.
     }    %
    \explanationdetail{\coloredbullet\ %
     Work with Product, Finance, People team, Support, and Marketing
     }    %
    \datedexperience{Bloomreach}{Jan 2017-Apr2019} 
    \explanation{Engineering Team Lead} 
    \explanationdetail{\coloredbullet\ %
    Team lead for a feature development team, focused on customer-facing improvements to the CMS.
     }
    %
    \datedexperience{Hippo, a Bloomreach Company}{Apr 2015-Jan 2017} 
    \explanation{Web Developer} 
    \explanationdetail{\coloredbullet\ %
     Hippo developer, focused on helping customers with their project implementation.
     }
    %
    \datedexperience{Oelan}{Aug 2013-Apr 2015} 
    \explanation{IT Specialist} 
    \explanationdetail{\coloredbullet\ %
     Lead full-stack developer for \href{https://www.privacyperfect.com}{PrivacyPerfect}, enabling companies to document their use of Personally Identifiable Data.
     }
     %
    \datedexperience{Ordina}{Aug 2011-Apr 2013} 
    \explanation{Java developer} 
    \explanationdetail{\coloredbullet\ %
     Junior Java developer, posted at the Rabobank.
     }
%
% Skills
\section{Skills}
    %
    \newcommand{\skillone}{\createskill{Software Development}{(Distributed) Scrum Methodology \cpshalf DevOps Lifecycles \cpshalf KanBan \cpshalf CICD}}
    %
    \newcommand{\skilltwo}{\createskill{People Management}{5x5 communication \cpshalf conflict resolution \cpshalf team-building \cpshalf 360 feedback empowerement}}
    %
    \newcommand{\skillthree}{\createskill{Cost \& Project Management}{AWS billing and cost monitoring \cpshalf Sysdig cost advisor \cpshalf Agile project management}}
    %
    \newcommand{\skillfour}{\createskill{Languages}{\textbf{\emph{Native:}} \ \  Dutch \ \ \textbf{\emph{Fluent:}} \ \ English }}
    %
    \createskills{\skillone, \skilltwo, \skillthree, \skillfour}
%
% Experience
%
%Education
\section{Education} 
    \datedexperience{University of Amsterdam}{2007-2011} 
    \explanation{PhD - Thesis title: Crime reconstruction in real-life surveillance videos} 
     \explanationdetail{\coloredbullet\ % 
     Not finished
     }
    \datedexperience{University of Amsterdam}{2004-2006} 
    \explanation{M.Sc in Artificial Intelligence} 
    \explanationdetail{\coloredbullet\ %
     International research master on autonomous systems
     }
    \datedexperience{University of Amsterdam}{2000-2004} 
    \explanation{B.Sc in Artificial Intelligence} 
    \explanationdetail{\coloredbullet\ %
     General Bachelor on Artificial Intelligence, part of the informatics department
     }
%
%Footnote
\createfootnote
\end{document}
